---
title: "SAM Dashboard"
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
params:
  bundle_path: ""
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(SAMutils)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)

bundle <- readRDS(params$bundle_path)

safe_plot <- function(expr, label = "Plot unavailable") {
  tryCatch(
    {
      p <- eval(expr)
      if (inherits(p, c("gg", "ggplot", "patchwork"))) {
        print(p)
      }
      invisible(NULL)
    },
    error = function(e) {
      print(
        ggplot() +
          annotate("text", x = 0, y = 0, label = label) +
          theme_void()
      )
      invisible(NULL)
    }
  )
}

safe_table <- function(x, max_rows = 200L, label = "No data") {
  if (is.null(x)) {
    return(data.frame(message = label))
  }
  x_df <- as.data.frame(x)
  if (nrow(x_df) == 0) {
    return(data.frame(message = label))
  }
  utils::head(x_df, max_rows)
}

render_table <- function(x, max_rows = 200L, label = "No data") {
  knitr::kable(
    safe_table(x, max_rows = max_rows, label = label),
    format = "html"
  )
}

render_conf_panel <- function(fit_obj) {
  conf_txt <- try(
    capture.output(stockassessment::saveConf(fit_obj$conf, file = "")),
    silent = TRUE
  )
  if (inherits(conf_txt, "try-error") || length(conf_txt) == 0) {
    conf_txt <- "Configuration unavailable."
  }

  conf_html <- paste(conf_txt, collapse = "\n")
  conf_html <- htmltools::htmlEscape(conf_html)
  cat(
    paste0(
      "<div style='border:1px solid #d9d9d9;border-radius:8px;background:#fafafa;",
      "padding:12px;max-height:520px;overflow:auto;'>",
      "<pre style='margin:0;white-space:pre;font-family:ui-monospace,SFMono-Regular,Menlo,Monaco,Consolas,monospace;",
      "font-size:12px;line-height:1.35;'>",
      conf_html,
      "</pre></div>"
    )
  )
}
```

# Overview

### Model Summary

```{r}
fit_obj <- bundle$res$fit
yr <- suppressWarnings(as.numeric(rownames(fit_obj$data$stockMeanWeight)))
age <- suppressWarnings(as.numeric(colnames(fit_obj$data$stockMeanWeight)))

summary_tbl <- data.frame(
  item = c(
    "Model name",
    "Years",
    "Ages",
    "Fleets",
    "Surveys",
    "Recruitment model code"
  ),
  value = c(
    "SAM fit",
    paste0(min(yr, na.rm = TRUE), "-", max(yr, na.rm = TRUE)),
    paste0(min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE)),
    nrow(fit_obj$conf$keyLogFpar),
    nrow(fit_obj$conf$keyVarObs) - 1,
    fit_obj$conf$stockRecruitmentModelCode
  ),
  stringsAsFactors = FALSE
)
render_table(summary_tbl, max_rows = 20)
```

### Configuration (`saveConf`)

```{r}
#| results: asis
render_conf_panel(bundle$res$fit)
```

# Input Data

## Tables {.tabset}

### Stock mean weight

```{r}
render_table(
  bundle$input_tables$stockMeanWeight,
  max_rows = 500,
  label = "stockMeanWeight unavailable"
)
```

### Catch mean weight

```{r}
render_table(
  bundle$input_tables$catchMeanWeight,
  max_rows = 500,
  label = "catchMeanWeight unavailable"
)
```

### Natural mortality

```{r}
render_table(
  bundle$input_tables$natMor,
  max_rows = 500,
  label = "natMor unavailable"
)
```

### Proportion mature

```{r}
render_table(
  bundle$input_tables$propMat,
  max_rows = 500,
  label = "propMat unavailable"
)
```

### Proportion fished

```{r}
render_table(
  bundle$input_tables$propF,
  max_rows = 500,
  label = "propF unavailable"
)
```

### Proportion natural mortality

```{r}
render_table(
  bundle$input_tables$propM,
  max_rows = 500,
  label = "propM unavailable"
)
```

### Landed fraction

```{r}
render_table(
  bundle$input_tables$landFrac,
  max_rows = 500,
  label = "landFrac unavailable"
)
```

### Discard mean weight

```{r}
render_table(
  bundle$input_tables$disMeanWeight,
  max_rows = 500,
  label = "disMeanWeight unavailable"
)
```

### Landed mean weight

```{r}
render_table(
  bundle$input_tables$landMeanWeight,
  max_rows = 500,
  label = "landMeanWeight unavailable"
)
```

# Model Fit

### Observation Residuals

```{r}
safe_plot(
  quote(model_resid_plot(bundle$res)),
  "Observation residuals unavailable"
)
```

### Process Residuals

```{r}
safe_plot(
  quote(model_pres_resid_plot(bundle$res)),
  "Process residuals unavailable"
)
```

### Combined Fit

```{r}
safe_plot(
  quote(model_combfit(bundle$res, bundle$model_dat)),
  "Combined fit unavailable"
)
```

### SI Plot

```{r}
safe_plot(quote(model_sifit_plot(bundle$res)), "SI plot unavailable")
```

# Standard Output

### Time Series

```{r}
safe_plot(
  quote(
    bundle$standard_output |>
      ggplot(aes(year, median)) +
      geom_ribbon(
        aes(ymin = lower, ymax = upper),
        alpha = 0.2,
        fill = "steelblue"
      ) +
      geom_line(linewidth = 0.5) +
      facet_wrap(~variable, scales = "free_y") +
      labs(x = "Year", y = "Estimate")
  ),
  "Standard output plot unavailable"
)
```

### Wide Table

```{r}
std_wide <- bundle$standard_output |>
  select(year, variable, median, lower, upper) |>
  pivot_wider(
    names_from = variable,
    values_from = c(median, lower, upper),
    names_glue = "{variable}_{.value}"
  ) |>
  arrange(year)
render_table(
  std_wide,
  max_rows = 500,
  label = "Standard output table unavailable"
)
```

# Diagnostics

### Likelihood

```{r}
safe_plot(quote(model_lik_plot(bundle$res)), "Likelihood plot unavailable")
```

### Selectivity

```{r}
safe_plot(
  quote(model_selectivity_plot(bundle$res)),
  "Selectivity plot unavailable"
)
```

### Stock-Recruit

```{r}
safe_plot(quote(SR_plot(bundle$res)), "Stock-recruit plot unavailable")
```

# Retro / Leave-Out

### Leave-Out

```{r}
safe_plot(quote(model_lo_plot(bundle$res)), "Leave-out plot unavailable")
```

### Retro

```{r}
safe_plot(quote(model_retro_plot(bundle$res)), "Retro plot unavailable")
```

# Annotated Parameters

```{r}
par_tbl <- try(annotated_par_table(bundle$res$fit), silent = TRUE)
if (inherits(par_tbl, "try-error")) {
  render_table(
    data.frame(message = "Annotated parameter table unavailable"),
    max_rows = 5
  )
} else {
  render_table(par_tbl, max_rows = 1000)
}
```
